Assessing Virulence by MCG

### 2017-08-22 doc/RMD/MCG-virulence.Rmd
Clean out a lot of old results
There were extra figures and tables littering the
results directory due to various things including
misspelling. These have been cleared.
modify MCG-virulence to use write_csv in pipe

```{r load_packages, message = FALSE, warning = FALSE}
library("tidyverse")
```

@@

```{r anova, fig.width = 4, fig.height = 8}
ANOVA <- aov(Severity ~ MCG, data = top_mcg)
ANOVA
summary(ANOVA)
plot(TukeyHSD(ANOVA, conf.level = 0.95), las = 2)
grps <- agricolae::HSD.test(ANOVA, "MCG", alpha = 0.05)$groups
readr::write_csv(grps, path = "results/tables/MCG-aggressiveness.csv", col_names = TRUE)

grps %>% 
  dplyr::rename(MCG = trt) %>%
  dplyr::rename(Group = M) %>%
  dplyr::rename(`Mean Aggressiveness` = means) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(row = huxtable::everywhere, col = 1, 0) %>% 
  huxtable::set_col_width(c(0.05, 0.3, 0.08)) %>%
  huxtable::set_align(row = huxtable::everywhere, col = 2, "right") %>%
  huxtable::print_md(max_width = 31)
```

@@

```{r anova2, fig.width = 4, fig.height = 8}
region_dat %>%
  group_by(Region) %>%
  summarize(N = n(), 
            `Min Aggressiveness` = min(Severity),
            `Max Aggressiveness` = max(Severity),
            `Average Aggressiveness` = mean(Severity),
            `Median Aggressiveness` = median(Severity)
            ) %>%
  knitr::kable(digits = 2)
ANOVA <- aov(Severity ~ Region, data = region_dat)
ANOVA
summary(ANOVA)
plot(TukeyHSD(ANOVA, conf.level = 0.95), las = 2)
grps <- agricolae::HSD.test(ANOVA, "Region", alpha = 0.05)$groups %>% 
  dplyr::rename(Region = trt) %>%
  dplyr::rename(Group = M) %>%
  dplyr::rename(`Mean Aggressiveness` = means)

readr::write_csv(grps, path = "results/tables/Region-aggressiveness.csv", col_names = TRUE)

grps %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(row = huxtable::everywhere, col = 1, 0) %>% 
  huxtable::set_col_width(c(0.13, 0.25, 0.08)) %>%
  huxtable::set_align(row = huxtable::everywhere, col = 2, "right") %>%
  huxtable::print_md(max_width = 40)
```

@@

```{r anova3, fig.width = 4, fig.height = 8}
top_mlg %>%
  group_by(MLG) %>%
  summarize(N = n(), 
            `Min Aggressiveness` = min(Severity),
            `Max Aggressiveness` = max(Severity),
            `Average Aggressiveness` = mean(Severity)
            ) %>%
  knitr::kable(digits = 2)
ANOVA <- aov(Severity ~ MLG, data = top_mlg)
ANOVA
summary(ANOVA)
plot(TukeyHSD(ANOVA, conf.level = 0.95), las = 2)
grps <- agricolae::HSD.test(ANOVA, "MLG", alpha = 0.05)$groups %>% 
  dplyr::rename(MLG = trt) %>%
  dplyr::rename(Group = M) %>%
  dplyr::rename(`Mean Aggressiveness` = means)

readr::write_csv(grps, path = "results/tables/MLG-aggressiveness.csv", col_names = TRUE)

grps %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(row = huxtable::everywhere, col = 1, 0) %>% 
  huxtable::set_col_width(c(0.13, 0.25, 0.08)) %>%
  huxtable::set_align(row = huxtable::everywhere, col = 2, "right") %>%
  huxtable::print_md(max_width = 40)
```

>>>>

```{r load_packages, message = FALSE, warning = FALSE}
library("tidyverse")
dir.create(file.path(PROJHOME, "results", "tables"))
```

@@

```{r anova, fig.width = 4, fig.height = 8}
ANOVA <- aov(Severity ~ MCG, data = top_mcg)
ANOVA
summary(ANOVA)
plot(TukeyHSD(ANOVA, conf.level = 0.95), las = 2)
grps <- agricolae::HSD.test(ANOVA, "MCG", alpha = 0.05)$groups

grps %>% 
  dplyr::rename(MCG = trt) %>%
  dplyr::rename(Group = M) %>%
  dplyr::rename(`Mean Aggressiveness` = means) %>%
  readr::write_csv(path = "results/tables/MCG-aggressiveness.csv", col_names = TRUE) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(row = huxtable::everywhere, col = 1, 0) %>% 
  huxtable::set_col_width(c(0.05, 0.3, 0.08)) %>%
  huxtable::set_align(row = huxtable::everywhere, col = 2, "right") %>%
  huxtable::print_md(max_width = 31)
```

@@

```{r anova2, fig.width = 4, fig.height = 8}
region_dat %>%
  group_by(Region) %>%
  summarize(N = n(), 
            `Min Aggressiveness` = min(Severity),
            `Max Aggressiveness` = max(Severity),
            `Average Aggressiveness` = mean(Severity),
            `Median Aggressiveness` = median(Severity)
            ) %>%
  knitr::kable(digits = 2)
ANOVA <- aov(Severity ~ Region, data = region_dat)
ANOVA
summary(ANOVA)
plot(TukeyHSD(ANOVA, conf.level = 0.95), las = 2)
grps <- agricolae::HSD.test(ANOVA, "Region", alpha = 0.05)$groups %>% 
  dplyr::rename(Region = trt) %>%
  dplyr::rename(Group = M) %>%
  dplyr::rename(`Mean Aggressiveness` = means) %>%
  readr::write_csv(path = "results/tables/Region-aggressiveness.csv", col_names = TRUE) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(row = huxtable::everywhere, col = 1, 0) %>% 
  huxtable::set_col_width(c(0.13, 0.25, 0.08)) %>%
  huxtable::set_align(row = huxtable::everywhere, col = 2, "right") %>%
  huxtable::print_md(max_width = 40)
```

@@

```{r anova3, fig.width = 4, fig.height = 8}
top_mlg %>%
  group_by(MLG) %>%
  summarize(N = n(), 
            `Min Aggressiveness` = min(Severity),
            `Max Aggressiveness` = max(Severity),
            `Average Aggressiveness` = mean(Severity)
            ) %>%
  knitr::kable(digits = 2)
ANOVA <- aov(Severity ~ MLG, data = top_mlg)
ANOVA
summary(ANOVA)
plot(TukeyHSD(ANOVA, conf.level = 0.95), las = 2)
grps <- agricolae::HSD.test(ANOVA, "MLG", alpha = 0.05)$groups %>% 
  dplyr::rename(MLG = trt) %>%
  dplyr::rename(Group = M) %>%
  dplyr::rename(`Mean Aggressiveness` = means) %>%
  readr::write_csv(path = "results/tables/MLG-aggressiveness.csv", col_names = TRUE) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(row = huxtable::everywhere, col = 1, 0) %>% 
  huxtable::set_col_width(c(0.13, 0.25, 0.08)) %>%
  huxtable::set_align(row = huxtable::everywhere, col = 2, "right") %>%
  huxtable::print_md(max_width = 40)
```
